Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-07-12 Manuscript/main.tex
Worked on partial plots

The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
% Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
Random intercepts were used to model variance at the field level (and plot level, for data collected within plots); however, plot-level variance terms 
% Plot-level RE omitted from: commodity pollen, commodity flwSurv, commodity seedCount, seed plDens 
% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function. (Move to appendix)
Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
Plant and pollen samples were not collected from male bays, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
% Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 81.6, df = 86, p = 0.62).
Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
Basis sets were generated using the \texttt{dagitty} library in R 3.5.1.

@@

All component GLMMs of the pSEM were written in Stan 2.17.1 \citep{gelman2015}, and run using \texttt{rstan} 2.18.1.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were adequately specified (p$\sim$0.5).
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).

>>>>

The underlying models of each pSEM were specified as generalized linear mixed-effects models (GLMMs, see Equation sets S1 and S2 for model specifications).
GLMMs can model processes that occur at different levels; for example, seed size was modelled at the plant level, while pollen deposition was modeled at the flower level.
% Random intercepts were used to model variance between fields, within-field (pollen, flower survival, seed count \& size), and within-plot (seed count \& size).
Random intercepts were used to model variance at the field level and plot level, but plot-level variance terms had poor traces and low effective sample sizes, indicating low variation within plots.
Therefore, we omitted plot-level random effects for the commodity field models of pollen deposition, flower survival, seeds per pod, and seed size, and omitted them from the seed field models of seeds per pod and seed size.
% Continuous responses were modeled using log-normal (plant density, plant size), square-root normal (flower density), and exponential-normal distributions (weight per seed), while counts were modeled as a negative-binomial (honey bee visits, pollen grains per stigma, flowers per plant, seeds per pod) or zero-inflated negative-binomial distribution (LCB visits) with a log-link function. (Move to appendix)
Visitation models used $log$(time) as an ``offset" variable to account for differences in observation times.
Plant and pollen samples were not collected from male bays in seed fields, and there were no large differences in visitation rates for honey bees or LCBs (p = 0.32, 0.72, respectively) once other terms were included as covariates, so bay identity was excluded from further analysis.
% Pod set (fraction of flowers that matured into pods) was modeled using a beta-binomial distribution with a logit-link function.
% Interactions between predictors were evident in honey bee visitation rate (Year:Locality interaction) and plant density (Irrigation:Year) in commodity canola, and for LCB visitation (Tent Stocking:Distance from edge) in seed canola, and were included in each model (represented as Y-shaped path in Figures \ref{fig:commoditySEM} and \ref{fig:seedSEM}).

Structural equation models do not have paths between all variables, which may bias the model results if this independence assumption is incorrect; this requires testing a ``basis set" of independence claims using Shipley's d-separation criteria \citep{shipley2000, shipley2009}.
The initial commodity canola pSEM was misspecfied, as several missing paths were identified (Fisher's C = 167.5, df = 64, p$<<$0.001), but the updated pSEM was deemed adequate (C = 81.6, df = 86, p = 0.62).
Similarly, the initial seed field pSEM also had several missing paths (C = 105.6, df = 76, p = 0.01), which were added, making the updated pSEM adequate (C = 72.2, k = 72, p = 0.47).
Basis sets were generated using the \texttt{dagitty} library in R 4.2.1.

@@

All component GLMMs of the pSEM were written in Stan 2.18.1 \citep{gelman2015} and run using \texttt{rstan} 2.26.13.
We used weakly informative normal priors ($\mu=0, \sigma=5$) for fixed effects and gamma priors ($\alpha=1, \beta=1$) for the variance components.
Four separate chains were run with an adaptive phase of 1000 iterations, and a sampling phase of 1000 iterations, then checked for convergence of the chains ($\hat{R} \approx$1) and low autocorrelation within chains (high $N_{eff}$).
We assessed the underlying probability distribution functions of each model using posterior predictive checks \citep{gelman2013}, and found that the probability distributions were properly specified (p$\sim$0.5).
% This means that while the average seed counts (per plant) were unbiased, the variance within a plant was not. 
% However, the negative binomial distribution had the closest posterior predictive checks of any other distribution. 
% p-values listed below (also in Tables S3 and S4) are \textit{posterior} p-values, representing the proportion of the posterior distribution that overlapped zero, with Z-scores (mean/standard deviation of posterior) showing the effect size.
% Predictions from models are median values of the posterior, representing the median prediction, while intervals displayed in figures are credible intervals (CIs), representing 95\% of the samples drawn from the posterior distribution (analogous to confidence intervals, see \citealt{gelman2013}).
